Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society

### 2024-02-24 manuscript/manuscript.qmd
Add caveats for research design
Why we're only looking at ROs and why that's okay

theme_set(theme_ongo())
set_annotation_fonts()
```

@@

Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental agency related to an INGO's issue area that oversees and co-supervises the INGO with provincial Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, as potential PSUs have no legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. INGOs vary in their ability to attract partner PSUs, and organizations that struggle to find suitable PSUs face limitations in their scope and geographic reach. After successfully gaining legal status, INGOs must follow the law's operational regulations, such as no fundraising within mainland China, only channeling funds through the RO's or PSU's bank accounts, filing reports regularly, and staying within the geographical and issue scopes as approved. INGOs undertaking temporary activities also need to find an eligible Chinese partner---including governmental, quasi-governmental, or non-profit organizations---and must keep their programs within approved limits, but the process is less onerous.

@@

To test the relationships between government preferences, INGO issue area, and INGO operational space, we apply this conceptual model to China's ONGO law. Previous research has looked at *A posteriori* (notes: I don't know if it is a correct use of latin words, I want to say how the INGO sector is like in a timeframe after the law) effects of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society. By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal restrictive INGO law has shaped the operational space for foreign organizations working in the country. Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the legal presence and potential reach of INGOs and reshape their issue areas. We conducted both a descriptive analysis of the composition of the issue areas of INGOs successfully registered under the INGO law and a regression analysis of the relationshp between INGO issue areas and their operational space.

@@

> **E~1~**: Because issue areas reflect varied level of contentiousneeds and government preferences, the number of provinces INGOs are approved to operate in is associated with their issue areas.

@@

We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered. Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status right after Jan. 1, 2017, the timing of registration for ROs varies by years. More time elapsed since the enforcement of the law can mean INGOs took more efforts to seek an ideal registration results, and they are more rest-assured to maintain a not-yet-legal status because they do not work in contentious issue areas. For example, World Animal Protection has been wording in China since 2007, but they did not register their office until two years after the ONGO Law took effect.

@@

Additionally, we introduced province fixed effects in the model to account for socio-economic or institutional differences across provinces, as well aw registration year fixed effects to account for any potential administrative processing variance during COVID years.

@@

Our data comes from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office, which maintains a website with complete documentation of all the ROs registered and temporary activities filed across China. We include all RO registrations between January 1, 2017, when the law took effect, to December 31, 2021, with information for all `r nrow(ongo)` actively registered organizations. The filing documents for ROs disclose each INGO's name, address, registration date, regulating Public Security Bureau, PSU, issue area and purposes of the RO, and the specific provinces they can work in. We merge this INGO data with translated English organization names from ChinaFile. Our data and reproducible code are available at `ANONYMIZED_DOI_URL`.

## Measurement and Descriptive Analysis

>>>>

theme_set(theme_ongo())
set_annotation_fonts()

# Manual TA stuff from other paper
n_ongos_ta <- 1019
n_ta <- 4011
```

@@

Registering as an RO under the ONGO Law is a complex process that requires the consent of a Chinese Professional Supervisory Unit (PSU)---a governmental or quasi-governmental agency related to an INGO's issue area that oversees and co-supervises the INGO with provincial Public Security Bureaus. Obtaining the consent of a PSU to apply for registration has become a key challenge for INGOs interested in formal registration, as potential PSUs have no legal obligation to assume such a demanding role [@Jia:2017; @Shieh:2018; @YeHuang:2018]. INGOs vary in their ability to attract partner PSUs, and organizations that struggle to find suitable PSUs face limitations in their scope and geographic reach. After successfully gaining legal status, INGOs must follow the law's operational regulations, such as no fundraising within mainland China, only channeling funds through the RO's or PSU's bank accounts, filing reports regularly, and staying within the geographical and issue scopes as approved. INGOs undertaking temporary activities also need to find an eligible Chinese partner---including governmental, quasi-governmental, or non-profit organizations---and must keep their programs within approved limits, but the process is less onerous. According to data from the Chinese Ministry of Public Security and ChinaFile [@ChinaFile:2022], between January 1, 2017 and December 31, 2021, `r nrow(ongo)` organizations obtained RO status, while `r scales::label_comma()(n_ongos_ta)` organizations submitted documentation for `r scales::label_comma()(n_ta)`. Nearly twice as many INGOs have opted for an easier, but far more restricted, pathway for legally operating in China.

@@

To test the relationships between government preferences, INGO issue area, and INGO operational space, we apply this conceptual model to China's ONGO law. Previous research has looked at *A posteriori* (notes: I don't know if it is a correct use of latin words, I want to say how the INGO sector is like in a timeframe after the law) effects of civil society laws on a global scale [@LianMurdie:2023; @Chaudhry:2022], which naturally blurs the specific policy mechanisms regimes use for controlling and leveraging global civil society. By analyzing the population of formally registered INGOs between 2017–2021, we can more precisely explore how a single formal restrictive INGO law has shaped the operational space for foreign organizations working in the country. Specifically, we can observe exactly how the Chinese government has used the RO registration process to strategically limit the legal presence and potential reach of INGOs and reshape their issue areas. We conducted both a descriptive analysis of the composition of the issue areas of INGOs successfully registered under the INGO law and a regression analysis of the relationship between INGO issue areas and their operational space.

@@

> **E~1~**: Because issue areas reflect varied level of contentiousness and government preferences, the number of provinces INGOs are approved to operate in is associated with their issue areas.

@@

We also took into account the temporal factor, the time elapsed since the law took effect when the ROs got registered. Since there was a *de facto* grace period for INGOs to seek registration even though theoretically all existing INGOs should obtain the legal status right after January 1, 2017, the timing of registration for ROs varies by years. More time elapsed since the enforcement of the law can mean INGOs took more efforts to seek an ideal registration results, and they are more rest-assured to maintain a not-yet-legal status because they do not work in contentious issue areas. For example, World Animal Protection has been wording in China since 2007, but they did not register their office until two years after the ONGO Law took effect.

@@

Additionally, we introduced province fixed effects in the model to account for socio-economic or institutional differences across provinces, as well as registration year fixed effects to account for any potential administrative processing variance during COVID years.

Before testing these expectations, we must first note a few important caveats. As discussed previously, international NGOs have two avenues for legally working in China: (1) formal registration as an RO and (2) ad hoc temporary activity (TA) status. The RO process is more costly and requires far more administrative and legal work, and as a result, nearly twice as many organizations have used temporary activities rather than formal registration. In this study, however, we do not look at patterns in TA use to explore INGO operational space. There is an incredible amount of variation in how TAs are used. Some organizations submit dozens of TA requests, possibly as a type of workaround to obtaining RO status, while others use them as true temporary activities, submitting requests for one-off conferences or workshops. INGOs using TAs thus do not work well as a test case of the relationship between INGO operational space and the de facto implementation of the ONGO law. More permanent ROs are more appropriate. Additionally, we cannot observe or measure the activities of INGOs that have not attempted to establish operations in the country or who left the country following the implementation of the ONGO law in 2017. The population of INGOs working with full, permanent legal status is thus limited only to organizations that have already been vetted as "safe" and acceptable by the government. Even under these conditions, though, we should expect to see variation in operational space, due to heterogeneity in both (1) government preferences and INGO issues (i.e. not all registered INGOs work on the same issues, and not all issues are of equal value or importance to the regime), and (2) INGO preferences and resources (i.e. not all INGOs have the same goals, missions, or resources).

@@

Our data comes from INGOs' public registration documents disclosed by the Ministry of Public Security's Overseas NGO Office, which maintains a website with complete documentation of all the ROs registered and temporary activities filed across China. We include all RO registrations between January 1, 2017, when the law took effect, to December 31, 2021, with information for all `r nrow(ongo)` actively registered organizations. The filing documents for ROs disclose each INGO's name, address, registration date, regulating Public Security Bureau, PSU, issue area and purposes of the RO, and the specific provinces they can work in. We merge this INGO data with translated English organization names from ChinaFile [@ChinaFile:2022]. Our data and reproducible code are available at `ANONYMIZED_DOI_URL`.

## Measurement and descriptive analysis
